CODECHECK: An open-science initiative for the independent execution of computations underlying research articles

### 2021-01-25 codecheck-paper.tex
fix some warnings in bibliography, fix latex error
add icons to authors

@@

\begin{document}
\title{CODECHECK: An open-science initiative for the independent execution of computations underlying research articles}
\author[1,$\ast$]{Daniel N\"{u}st}
\author[2,$\ast$]{Stephen J Eglen}
\affil[1]{\url{https://orcid.org/0000-0002-0024-5046}}
\affil[2]{\url{https://orcid.org/0000-0001-8607-8025}}
\affil[$\ast$]{Contributed equally}
\affil[$$]{Public project for this article is at \url{https://github.com/codecheckers/paper}}
\maketitle
\begin{abstract}
  This is a draft paper that we hope to submit to F1000R (and perhaps
  as a preprint before) in the coming weeks.
  \ldots{}
\end{abstract}

@@

Going beyond article types, the journal \emph{ReScience C} publishes only
replications\footnote{\url{https://rescience.github.io/faq/}} requiring
open code and replication by a third party to. ReScience also relies on
free infrastructure (GitHub and Zenodo).
For research with very high stakes, where reproduction would be too weak and
post publication replication possibly too late because of policy impact,
Benjamin-Chung et~al. \cite{benjamin-chung_internal_2020} propose
\emph{internal replication}.
A workflow that underwent internal
replication would very likely be of high quality and relatively easy to check.
Similarly, internal CODECHECKs may be used, with the same limitations such
as group think \cite{benjamin-chung_internal_2020},
to ensure reproducibility before submission.
Such internal checks are professionalised in local reproduction services,
such as CISER R-squared\footnote{
\url{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/}},
} (established/permanent),
%Uni Münster's Reproducible Research Support Service\footnote{
%\url{https://go.wwu.de/r2s2}} (pilot),
Oxford's code review network (OxCRN)\footnote{
\url{https://github.com/OxfordCodeReviewNet/forum}} (community, broader scope), or
Yale's YARD\footnote{
\url{https://isps.yale.edu/research/data/approach}} (staff for replications).

>>>>

\usepackage{academicons} % for ORCID icon, via https://tex.stackexchange.com/a/534476/212961
\definecolor{idcolor}{HTML}{A6CE39}
\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{\color{idcolor}\aiOrcid}}

\newcommand{\email}[1]{\href{mailto:#1}{#1}}

\usepackage{fontawesome}
\newcommand{\github}[1]{\href{https://github.com/#1}{\faGithub}}
\newcommand{\twitter}[1]{\href{https://twitter.com/#1}{\faTwitter}}

@@

\begin{document}
\title{CODECHECK: An open-science initiative for the independent execution of computations underlying research articles}
\author[1,$\ast$]{Daniel~N\"{u}st \orcid{0000-0002-0024-5046} \github{nuest} \twitter{nordholmen}}
\author[2,$\ast$]{Stephen~J~Eglen \orcid{0000-0001-8607-8025} \github{sje30} \twitter{StephenEglen}}
\affil[1]{Institute for Geoinformatics, University of M\"unster, Germany; \email{daniel.nuest@uni-muenster.de}}
\affil[2]{Department of Applied Mathematics and Theoretical Physics, University of Cambridge, GB; \email{sje30@cam.ac.uk}}
\affil[$\ast$]{Contributed equally}
\affil[$$]{Public project for this article is at \url{https://github.com/codecheckers/paper}}
\maketitle
\begin{abstract}
  This is a draft paper that we hope to submit to F1000R (and perhaps
  as a preprint before) in the coming weeks.
  \ldots{}
\end{abstract}

@@

Going beyond article types, the journal \emph{ReScience C} publishes only
replications\footnote{\url{https://rescience.github.io/faq/}} requiring
open code and replication by a third party to. ReScience also relies on
free infrastructure (GitHub and Zenodo).
For research with very high stakes, where reproduction would be too weak and
post publication replication possibly too late because of policy impact,
Benjamin-Chung et~al. \cite{benjamin-chung_internal_2020} propose
\emph{internal replication}.
A workflow that underwent internal
replication would very likely be of high quality and relatively easy to check.
Similarly, internal CODECHECKs may be used, with the same limitations such
as group think \cite{benjamin-chung_internal_2020},
to ensure reproducibility before submission.
Such internal checks are professionalised in local reproduction services,
such as CISER R-squared\footnote{
\url{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/}} (established/permanent),
%Uni Münster's Reproducible Research Support Service\footnote{
%\url{https://go.wwu.de/r2s2}} (pilot),
Oxford's code review network (OxCRN)\footnote{
\url{https://github.com/OxfordCodeReviewNet/forum}} (community, broader scope), or
Yale's YARD\footnote{
\url{https://isps.yale.edu/research/data/approach}} (staff for replications).
